Toronto Beach Data

### 2024-09-26 paper/paper.qmd
Introduction Completed

---
title: "Toronto Beach Data"
subtitle: "Data Analysis of the Relationship Between Date, Air Temperature, Whether It Rains or Not, Water Temperature, and Observations of Water Fowls"
author: "Yanzun Jiang"
date: today
date-format: long
thanks: "Code and data supporting this analysis is available at: https://github.com/Stary54264/Toronto-Beach-Data"
abstract: "This paper conducted a basic data analysis on data of beaches in Toronto. The variables mentioned in the tile are highly correlated. The analysis can help us to know better about beaches in Toronto. Further, it helps meteorologists to monitor climate changes."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

We use @citeR and @opendatatoronto.

The remainder of this paper is structured as follows.

@sec-data
@sec-data-1
@sec-data-2
@sec-data-2-1
@sec-data-2-2
@sec-data-2-3
@sec-data-2-4
@sec-results
@sec-discussion

@@

## Preview of data {#sec-data-1}

@@

## Visualization of the Distribution of Each Observed Variable {#sec-data-2}

This part shows the distributions of each observed variables using histograms.

### Air Temperature {#sec-data-2-1}

@@

### Rain {#sec-data-2-2}

@@

### Water Temperature {#sec-data-2-3}

@@

### Observations of Water Fowls {#sec-data-2-4}

@@

## First discussion point {#sec-first-point}

@@

## Dataset and Graph Sketches {#sec-appendix-1}

@@

## Data Cleaning {#sec-appendix-2}

>>>>

---
title: "Toronto Beach Data"
subtitle: "Data Analysis of the Relationship Between Date, Air Temperature, Whether It Rains or Not, Water Temperature, and Observations of Water Fowls"
author: "Yanzun Jiang"
date: today
date-format: long
thanks: "Code and data supporting this analysis is available at: <https://github.com/Stary54264/Toronto-Beach-Data>"
abstract: "This report analyzes environmental data collected in the summer of 2023 regarding Toronto's beaches, focusing on variables such as air temperature, water temperature, rainfall, and waterfowl observations. The findings reveal that ?increased water temperatures correlate with higher waterfowl activity, while rainy conditions tend to reduce sightings?. These insights emphasize the importance of understanding how weather patterns affect wildlife behavior and beach usability, suggesting that public awareness and management strategies should be adapted accordingly. Future research should explore the impact of these environmental factors on beachgoer experiences and the broader ecological implications."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

@@

In 2014, Toronto experienced an extremely cold summer that impacted its beaches @torontoweather. During this period, data on key environmental factors, such as air temperature, water temperature, rainfall, and observations of waterfowl activity, was collected at various beaches across the city @opendatatoronto. These factors are critical as they directly influence the ecological balance of the beaches, the safety of recreational activities, and the overall enjoyment of beachgoers @weatherandbeach.

Consequently, analyzing this environmental data is essential to understanding how these variables affect the behavior of waterfowl and the suitability of the beaches for public use. According to @temperatureandwaterfowl, waterfowl presence can be influenced by temperature changes, precipitation, and human activity on the beaches. This study focuses on examining the relationships between air temperature, water temperature, rainfall, and waterfowl observations, and how these conditions might correlate with fluctuations in bird activity and potential impacts on beachgoers.

To conduct this analysis, a dataset collected by @opendatatoronto was utilized, as described in @sec-data. Based on the initial findings, it was observed that ???higher water temperatures coincided with an increase in waterfowl activity, while rainy days led to a decrease in sightings ???(@sec-results). As discussed in @sec-discussion, ???these trends highlight the potential for waterfowl to congregate under specific environmental conditions, potentially affecting beach safety and cleanliness. Further recommendations include improving public awareness of how wildlife interactions and weather patterns influence beach environments???. This paper's structure includes an overview of the data and methods in @sec-data, the results of the analysis in @sec-results, a detailed discussion of the results in @sec-discussion, and supplementary insights in @sec-appendix.

@@

## Overview

### Preview of the Dataset

@@

### Air Temperature

@@

### Rain

@@

### Water Temperature

@@

### Observations of Water Fowls

@@

## First discussion point

@@

## Graph and Sketches

@@

## Data Cleaning
